Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
test-shouldbe

\noindent All combinators introduced in Section~\ref{sec:code-doc} have been
implemented.  They are available from Hackage\footnote{%
http://hackage.haskell.org/package/test-shouldbe},
and will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.

>>>>

\noindent All combinators introduced in Section~\ref{sec:code-doc} have been
implemented.  They are available from Hackage\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe},
and will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.
